### 2018-03-14 pubs/itp-2018/sections/proof-reconstruction.tex
ITP 2018: Initial commit.
Review section 4.2

With the \TSTP derivation from Step~2, we process the derivation with the
\Athena translator tool.
\Athena parses the \TSTP format, analyzes the
derivation and generates a representation of the natural deduction
proof using a tree data structure (see the properties
of this tree in Section~\ref{ssec:metis-proofs}).
In the \Athena analysis, some unnecessary steps that introduce redundancies
and some unused input are removed from the proof-tree.
As result, we get from \Athena an \Agda file of the proof
with names of functions and theorems from
the \Agda libraries that accompany this article:
\texttt{agda-prop} and \texttt{agda-metis}.

@@

In this section, we reconstruct each \Metis inference rule in
Table~\ref{tab:agda-metis-table}.
We begin describing the reconstruction of the \strip inference rule
since this rule  is the only one that closely follows the \Metis
source code.

To reconstruct the other rules, we use for their formalization
a pattern in their description and definition,
see Example~\ref{ex:inference-rule-pattern}.

\begin{notation}
  The function name written in \texttt{typewriter} font refers to a
  \Metis inference rule in the \TSTP derivations. The same function
  name written using
  \textsf{sans serif} font refers to our formalized version to
  reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
  To increase the readability of our formal descriptions in
  functions and theorems, we adopt
  the convention to use \Source and \Target as synonyms of the \Prop
  type. The \Source type in the reconstructed rule definition refers
  to the argument in the \TSTP derivation, \ie the input formula of
  the inference rule. A formula of \Target type refers to the
  expected result of the rule found in the \TSTP derivation.
\end{notation}

>>>>

With a \TSTP derivation file, we process the derivation with the
\Athena translator tool.
\Athena parses the \TSTP format, analyzes the
derivation and generates a representation of the natural deduction
proof using a tree data structure (see the properties
of this tree in Section~\ref{ssec:metis-proofs}).
In the \Athena analysis, some unnecessary steps that introduce redundancies
and some unused input are removed from the proof-tree.
As result, we get from \Athena an \Agda file of the proof
with names of functions and theorems from
the \Agda libraries that accompany this article:
\texttt{agda-prop} and \texttt{agda-metis}.

@@

In this section, we reconstruct each \Metis inference rule in
Table~\ref{tab:agda-metis-table}.
We begin describing the reconstruction of the \strip inference rule
since this rule  is the only one that closely follows the \Metis
source code. To reconstruct the other rules, we use a pattern for their
formalization showed in Example~\ref{ex:inference-rule-pattern}.

\begin{notation}
  The function name written in \texttt{typewriter} font refers to a
  \Metis inference rule in the \TSTP derivations. The same function
  name written using
  \textsf{sans serif} font refers to our formalized version to
  reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
  To increase the readability for functions and theorems, we use
  the convention \Source and \Target as synonyms of the \Prop
  type. The \Source type in the reconstructed rule definition refers
  to the argument in the \TSTP derivation, \ie the input formula of
  the inference rule. A formula of \Target type refers to the
  expected result of the rule found in the \TSTP derivation.
\end{notation}
